Decomposition-based Job-shop Scheduling with Constrained Clustering

### 2021-10-11 Artificial Intelligence and Machine Learning/PADL_conference/Paper_draft_v1.tex
discussion

@@

%It can be assumed that knowledge management is a crucial issue in the industry. To extract implicit, unknown, and potentially useful information from data, we use data mining techniques that have been responsible for many of artificial intelligence’s recent successes. 
%Clustering is one of these techniques, which is applied whenever the extracted data is not labeled, i.e., the semantics of this data is with respect to the application is unclear. Therefore, clustering has always been an exploratory but critical task in the knowledge discovery process, with applications ranging from image processing, production systems, and information retrieval \cite{benabdellah2019survey}. Clustering is a technique that aims to partition a dataset (objects) into subsets by identifying similar objects and aggregating them in the same cluster while the dissimilar objects should belong to different clusters.\\

@@

Some of the previous work \cite{koonce2000using, harrath2002genetic, shahzad2010discovering, ismail2012production, adibi2014clustering, nasiri2019data} have extracted the following features: priority, processing time, remaining processing time, machine load, and route position. Most of the researchers converted the attributes into qualitative data. As mentioned in these studies, the main reason for this conversion is to make the decision rules more generic, which can be applied to several scheduling problems. However, in our case, we will not convert the data into classes because we will use these features to measure the similarities/dissimilarities between the operations in the clustering process, which requires having numerical values.
We present the features that we considered:
%\paragraph{Process.}
%The two attributes \textit{Processing Time (PT)}  and \textit{Remain Processing Time (RPT)} are dependent on the problem domain. The \textit{PT} represents the execution time of a particular operation in a machine. However, \textit{RPT} is the aggregate processing time for all subsequent operations of that job. \todo[inline]{we need to provide rationale behind the features, why do we think they are useful for the clusering algorithm. Example of values extracted for the sample instance in Table 1 would also improve the readability of the paper.}
%\todo[inline]{Why in all other paragraphs we are talking only about one feature at a time and here about two. Can we split them? Like \\paragraph\{Processing Time (PT)\} and \\paragraph\{Remain Processing time (RPT)\}}
\paragraph{Processing Time (PT):}
The \textit{PT} represents the execution time of a particular operation in a machine.

\paragraph{Remain Processing Time (RPT):}
\textit{RPT} attribute is the aggregate processing time for all subsequent operations of that job.

\paragraph{Operation:}
The \textit{operation} attribute is an ordinal value to represent the rank of each operation in its job.

\paragraph{Time Length of a Job (TLJ):}
\textit{TLJ} is an attribute that describes the total processing time needed to complete a particular job. It is the summation of processing time for all operations of that job.

\paragraph{Earliest Starting Time (EST):}
The \textit{EST} attribute represents the earliest possible time for a particular operation to be executed. It is calculated by accumulating the processing time of the predecessor(s) of that operation, and it is $Zero$, if the operation has no predecessor.

\paragraph{{Machine Load} (ML):}
\textit{ML} is a property of a machine that shows how much time a particular machine has to execute all the operations assigned to it. In the initial state, the \textit{ML} is the aggregate of processing time of all operations assigned to that machine. For each step, the load of a machine is decreased by the processing time of an operation assigned to the machine and has the smallest \textit{EST}.

\paragraph{{Starting Time} (ST):}
\textit{ST} attribute represents the starting execution time of each operation by solving the problem using heuristics FIFO, MTWR and EST developed by \cite{tassel2021reinforcement,el2020job}.

\paragraph{{Waiting Time} (WT):}
Since we used three different heuristics to mine information from the obtained solution, we will have three waiting times. \textit{WT} attribute is the difference between the starting time of a particular operation and the maximum value between the end time of its predecessor and when the machine became free. \\

The following Table~\ref{tab3} shows a sample of the features that we extracted for the decomposition process. Each row in the table represents an operation, and it contains its value according to each feature. The second column shows the \textit{Remain Processing Time (RPT)} of a job. For instance, the first job $J_1$ consists of $3$ operations with a total processing time of $17$. In the beginning, the \textit{Remain Processing Time} of $O_{1,1}$ is $17$ because no operations are executed. After finishing the first operation of job $1$, the \textit{RPT} became $8$ because the processing time of the completed operation $O_{1,1}$ is excluded. When the second operation of job $1$ is completed, the \textit{RPT} of that job is $5$. \\

>>>>

\newcommand{\stest}{\textit{ST\_EST}}

@@

%It can be assumed that knowledge management is a crucial issue in the industry. To extract implicit, unknown, and potentially useful information from data, we use data mining techniques that have been responsible for many of artificial intelligence's recent successes. 
%Clustering is one of these techniques, which is applied whenever the extracted data is not labeled, i.e., the semantics of this data is with respect to the application is unclear. Therefore, clustering has always been an exploratory but critical task in the knowledge discovery process, with applications ranging from image processing, production systems, and information retrieval \cite{benabdellah2019survey}. Clustering is a technique that aims to partition a dataset (objects) into subsets by identifying similar objects and aggregating them in the same cluster while the dissimilar objects should belong to different clusters.\\

@@

Some of the previous work \cite{koonce2000using, harrath2002genetic, shahzad2010discovering, ismail2012production, adibi2014clustering, nasiri2019data} have extracted the following features: priority, processing time, remaining processing time, machine load, and route position. Most of the researchers converted the attributes into qualitative data. As mentioned in these studies, the main reason for this conversion is to make the decision rules more generic, which can be applied to several scheduling problems. However, in our case, we will not convert the data into classes because we will use these features to measure the similarities/dissimilarities between the operations in the clustering process, which requires having numerical values.
We present the features that we considered:
%\paragraph{Process.}
%The two attributes \textit{Processing Time (PT)}  and \textit{Remain Processing Time (RPT)} are dependent on the problem domain. The \textit{PT} represents the execution time of a particular operation in a machine. However, \textit{RPT} is the aggregate processing time for all subsequent operations of that job. \todo[inline]{we need to provide rationale behind the features, why do we think they are useful for the clusering algorithm. Example of values extracted for the sample instance in Table 1 would also improve the readability of the paper.}
%\todo[inline]{Why in all other paragraphs we are talking only about one feature at a time and here about two. Can we split them? Like \\paragraph\{Processing Time (PT)\} and \\paragraph\{Remain Processing time (RPT)\}}
\begin{description}
  \item[Processing Time (PT)] that represents the execution time of a particular operation in a machine.

  \item[Remaining Processing Time (RPT)] attribute corresponds to the total processing time for all subsequent operations of a job.

  \item[Operation (OP)] feature is an ordinal value representing the rank of each operation in its job.

  \item[Time Length of a Job (TLJ)] is an attribute describing the total processing time needed to execute all operations of a job. 
  %It is the summation of processing time for all operations of that job.

  \item[Earliest Starting Time (EST)] attribute represents the earliest possible execution time for an operation. It is calculated by accumulating the processing time of all preceding operations. This feature has a specific value $\mathit{Zero}$ if the operation has no predecessors.

  \item[Machine Load (ML)] is a property of a machine that shows how much time this machine requires to execute all the operations assigned to it. In the initial state, \textit{ML} corresponds to the total processing time of all operations assigned to that machine. For each step, the load of a machine is decreased by the processing time of an operation assigned to the machine and has the smallest \textit{EST}.

  \item[Starting Time (ST)] is a set of features representing the starting execution time of each operation by solving the problem using a heuristic. In our work, we consider EST (\stest), First-In-First-Out (ST\_FIFO), and Most Total Work Remaining (ST\_MTWR), see \cite{overview} for an overview.
  To compute the starting time, we use a simple greedy algorithm \cite{tassel2021reinforcement,el2020job}, that at each step selects a not scheduled operation according to the heuristics and schedules it to a machine. In the case of FIFO, the algorithm selects an operation that appeared first in the queue. Similarly, for MTWR ...

  \item[Waiting Time (WT)] is also a set of features, like ST, for which computation we used three different heuristics EST (WT\_EST), FIFO (WT\_FIFO), and MTWR (WT\_MTWR). Each feature in \textit{WT} set is the difference between the scheduled starting time of a particular operation and its earliest possible starting time. The latter is the maximum out of the end processing time of the operation's predecessor and the time at which the required machine became available.
\end{description}

The following Table~\ref{tab3} shows a sample of the features that we extracted for the decomposition process. Each row in the table represents an operation, and it contains its value according to each feature. The second column shows the \textit{Remaining Processing Time (RPT)} of a job. For instance, the first job $J_1$ consists of $3$ operations with a total processing time of $17$. In the beginning, the \textit{RPT} of $O_{1,1}$ is $17$ because no operations are executed. After finishing the first operation of job $1$, the \textit{RPT} became $8$ because the processing time of the completed operation $O_{1,1}$ is excluded. When the second operation of job $1$ is completed, the \textit{RPT} of that job is $5$. \\
